---
title: "__Data for Pollock, White Hake, and Red Hake to be implemented in HYDRA__"
output: html_document
---
# Growth Curves for Pollock, White Hake, and Red Hake

__Weight/Length__

The relationship between length and weight for these species as expressed by $W=a*L^b$ 

__Age/Length__

The von Bertalanffy growth curve was used to find the relationship between age and length using K and $L_{inf}$ as argument $L_{inf}*(1-exp(-k*t)$ for the following species.

## Pollock
 

The relationship between Pollock length (cm) and weight (lbs). The data was collected during NEFSC research bottom trawl surveys from 1992 to 1999. For the autumn surveys which were conducted from Cape Hatteras, North Carolina to Nova Scotia, Canada a= 0.000007244 and b= 3.1151 (Wigley et al., 2003). Winter/Spring surveys were conducted from Cape Hatteras, North Carolina to the Southern Flank of George's Bank a= 0.000006788 and b= 3.1024.

```{r pollockweight, echo=FALSE}
source("Weight:Length/LWformula.R") # <- function for Length Weight formula
datafile <-  read.csv(file="Weight:Length/Pollock_SV.csv", header=TRUE, sep=",")
modifiedData <- datafile[,c("INDWT","LENGTH")] # <- only wanted to compare weight (INDWT) and length

#Finding the sample size and removing any incomplete rows (taking out the NAs)
n <- length(modifiedData$INDWT) -sum(is.na(modifiedData$INDWT))

##Pollock
op = par(mfrow=c(1,1))

#Cape Hatteras to Nova Scotia (Autumn)
p_a<- 0.000007244
p_b <- 3.1151
p_L <- 0:130

#Cape Hatteras, NC to southern flank of George's Bank (Winter/Spring)
p_a2<- 0.000006788
p_b2 <- 3.1024
p_L2 <- 0:130

#Inserting the variables into the formula
CH2NSAutumn <- LWformula(a=p_a,b=p_b,L=p_L)
CH2GBWinterSpring <- LWformula(a=p_a2,b=p_b2,L=p_L2)
#Plotting
  #Autumn

plot(CH2NSAutumn,type="l", xlab= "Length (cm)",
     ylab= "Weight (lbs)", col=c("red"))
  #Winter/spring
lines(CH2GBWinterSpring, col=c("blue"))
  #Survey Data
points(modifiedData$LENGTH,modifiedData$INDWT*2.2046)
title(main="Pollock (L_nf=130cm)")
legend(0,60, legend=c("Cape Hatteras, NC to Nova Scotia (Autumn)", "Cape Hatteras, NC to southern flank of George's Bank (Winter/Spring)", 
                      paste("Survey Data (n=",n,")")), col=c("red", "blue", "black"), lty= c(1,1,NA), pch=c(NA,NA,1), cex=0.8)
```

The relationship between Pollock age (yrs) and length (cm) calculated by the von Bertalanffy growth rate for Nova Scotia, Canada where K= 0.1 and in the Northwest Atlantic, Canada where K= 0.17 (Erzini, 1991). These growth rates are compared to commercial fishing data gathered from 1976 to 2018 as well as survey data gathered by NEFSC.


```{r pollockage, echo=FALSE}
source("Growth/growth_curve_function.R") # <- created a function to calculate Von Bertanalanfy growth curve using K and Linf as arguments on another sheet
#Importing data from Commerical Fisheries (CF)
datafile <-  read.csv(file="Growth/pollockData_CF.csv", header=TRUE, sep=",")
modifiedData <- datafile[,c("AGE","LENGTH")]
datafileSV <- read.csv(file="Growth/pollockData_SV.csv", header=TRUE, sep=",")
modifiedSV <- datafileSV[,c("AGE", "LENGTH")]

#Sample size of survey and commercial fisheries data
nSV <- length(modifiedSV$AGE) -sum(is.na(modifiedSV$AGE))
nCF <- length(modifiedData$AGE) - sum(is.na(modifiedData$AGE))

## Pollock
  #Option1
p_Linf <- 130
p_K1 <- 0.17
p_K2 <- 0.1
p_t <- 0:30
Lengthof_p1 <- p_Linf*(1-exp(-p_K1*p_t))
Lengthof_p2 <- p_Linf*(1-exp(-p_K2*p_t))
  #Option2
Lengthof_p1 <- growthCurve(t= 0:30, k= 0.17, Linf= 130)
Lengthof_p2 <- growthCurve(t= 0:30, k= 0.1, Linf= 130)

##Plotting the Growth curve
plot(0:30,Lengthof_p1,type="l", xlab= "Age (years)", ylab= "Length (cm)", col=c("red"))
lines(p_t, Lengthof_p2, type= "l", col=c("blue"))
  #Plotting CFData
points(modifiedData$AGE,modifiedData$LENGTH)
  #Plotting Survey Data
points(modifiedSV$AGE,modifiedSV$LENGTH, pch=0)
title(main="Pollock (L_nf=130cm)")
legend(11,40, legend=c("Nova Scotia, CA (K=0.1)", "Northwest Atlantic, CA (K=0.17)",
                       paste("Commercial Fishing Data (1976-2018, n=",nCF,")"),
                       paste("Survey Data (n=",nSV,")")),col=c("red", "blue", "black", "black"),
                             lty= c(1,1, NA, NA), pch= c(NA, NA, 1, 0), cex=0.8)
```

The relationship between red hake length (cm) and weight (lbs). The data was collected during NEFSC research bottom trawl surveys from 1992 to 1999. For the autumn surveys which were conducted from Cape Hatteras, North Carolina to Nova Scotia, Canada a= 0.000005976951 and b=3.0162 (Wigley et al., 2003). Winter and spring surveys were conducted from Cape Hatteras, North Carolina to the Southern Flank of George's Bank. For the winter surveys a= 0.000006788 and b= 3.1024. For the spring surveys a= 0.000004225 and b= 3.0979.


## Red Hake

```{r redhake, echo=FALSE}
##RedHake
source("Weight:Length/LWformula.R")
datafile <-  read.csv(file="Weight:Length/redhake_SV.csv", header=TRUE, sep=",")
modifiedData <- datafile[,c("INDWT","LENGTH")]

#sample size
n <- length(modifiedData$INDWT) -sum(is.na(modifiedData$INDWT))

op = par(mfrow=c(1,1))

#Cape Hatteras to Nova Scotia (Autumn)
p_a<- 0.000005976951
p_b <- 3.0162
p_L <- 0:66
#CH to GB (winter)
p_a2<- 0.000004737
p_b2 <- 3.0661
p_L2 <- 0:66
#CH to GB (spring)
p_a3<- 0.000004225
p_b3 <- 3.0979
p_L3 <- 0:66

#LWformula(a=p_a,b=p_b,L=p_L)
CH2NSAutumn <- LWformula(a=p_a,b=p_b,L=p_L)
CH2GBWinter <- LWformula(a=p_a2,b=p_b2,L=p_L2)
CH2GBSpring <- LWformula(a=p_a3,b=p_b3,L=p_L3)

plot(CH2NSAutumn,type="l", xlab= "Length (cm)", ylab= "Weight (lbs)", col=c("red"))
lines(CH2GBWinter, col=c("blue"))
lines(CH2GBSpring, col=c("green"))
#Survey data
points(modifiedData$LENGTH,modifiedData$INDWT*2.2046)

title(main="Red Hake (L_nf=66cm)")
legend(0,4.1, legend=c("Cape Hatteras, NC to Nova Scotia (Autumn)", "Cape Hatteras, NC to southern flank of George's Bank (Winter)", "Cape Hatteras, NC to southern flank of George's Bank (Spring)", 
                      paste("Survey Data (n=",n,")")), col=c("red", "blue", "green", "black"), lty= c(1,1,1,NA), pch=c(NA,NA,NA,1), cex=0.8)
```

The relationship between red hake age (years) and length (cm) calculated by the von Bertalanffy growth rate for the North West Atlantic where K= 0.19 (Erzini, 1991). These growth rates are compared to survey data gathered by NEFSC.

```{r redhakeage, echo=FALSE}
##REDHAKE
source("Growth/growth_curve_function.R")
datafile <-  read.csv(file="Growth/redhake_SV.csv", header=TRUE, sep=",")
modifiedData <- datafile[,c("AGE","LENGTH")]

#sample size
n <- length(modifiedData$AGE) -sum(is.na(modifiedData$AGE))

rh_Linf <- 66
rh_K1 <- 0.19
rh_t <- 0:30
#Lengthof_rh1 <- rh_Linf*(1-exp(-rh_K1*rh_t))
Lengthof_rh1 <- growthCurve(t= 0:30, k= 0.19, Linf= 66)
rh_pointst <- c(1,2,3)
rh_pointsl <- c(8,13,16)

#north west atlantic
plot(rh_t,Lengthof_rh1, type="l", xlab= "Age (years)", ylab= "Length (cm)",col=c("red"))
#survey data
points(modifiedData$AGE, modifiedData$LENGTH)

title(main="Red Hake (L_inf= 66cm)")
legend(17,20, legend=c("North West Atlantic, US (K=0.19)",
                       paste("Survey Data (n=",n,")")),col=c("red", "black"),
       lty=c(1,NA),pch= c(NA, 1), cex=0.8)
```



## White Hake

The relationship between white hake length (cm) and weight (lbs). The data was collected during NEFSC research bottom trawl surveys from 1992 to 1999. For the autumn surveys which were conducted from Cape Hatteras, North Carolina to Nova Scotia, Canada a= 0.000004119 and b=3.1715 (Wigley et al., 2003). Winter and spring surveys were conducted from Cape Hatteras, North Carolina to the Southern Flank of George's Bank. For the winter surveys a= 0.000001904 and b= 3.3669. For the spring surveys a= 0.000002376 and b= 3.2903.

```{r whitehake, echo=FALSE}
source("Weight:Length/LWformula.R")
datafile <-  read.csv(file="Weight:Length/whitehake_SV.csv", header=TRUE, sep=",")
modifiedData <- datafile[,c("INDWT","LENGTH")]

#Sample size
n <- length(modifiedData$INDWT) -sum(is.na(modifiedData$INDWT))

## White Hake
op = par(mfrow=c(1,1))

#Cape Hatteras to Nova Scotia (Autumn)
p_a<- 0.000004119
p_b <- 3.1715
p_L <- 0:133

#Winter
p_a2<- 0.000001904
p_b2 <- 3.3669
p_L2 <- 0:133

#Spring
p_a3<- 0.000002376
p_b3 <- 3.2903
p_L3 <- 0:133
#LWformula(a=p_a,b=p_b,L=p_L)
CH2NSAutumn <- LWformula(a=p_a,b=p_b,L=p_L)
CH2GBWinter <- LWformula(a=p_a2,b=p_b2,L=p_L2)
CH2GBSpring <- LWformula(a=p_a3,b=p_b3,L=p_L3)

plot(CH2NSAutumn,type="l", xlab= "Length (cm)", ylab= "Weight (lbs)", col=c("red"))
lines(CH2GBWinter, col=c("blue"))
lines(CH2GBSpring, col=c("green"))
#Survey data
points(modifiedData$LENGTH,modifiedData$INDWT*2.2046)

title(main="White Hake (L_nf= 133cm)")
legend(0,50, legend=c("Cape Hatteras, NC to Nova Scotia (Autumn)", "Cape Hatteras, NC to southern flank of George's Bank (Winter)", "Cape Hatteras, NC to southern flank of George's Bank (Spring)", 
                     paste("Survey Data (n=",n,")")), col=c("red", "blue", "green", "black"), lty= c(1,1,1,NA), pch=c(NA,NA,NA,1), cex=0.8)
source("Growth/growth_curve_function.R")
#datafile <-  read.csv(file="whitehake_SV.csv", header=TRUE, sep=",")
modifiedData <- datafile[,c("AGE","LENGTH")]

#Calculating sample size
n <- length(modifiedData$AGE) -sum(is.na(modifiedData$AGE))
```

The relationship between white hake length and age calculated by the von Bertalanffy growth rate in two instances for the Southern Gulf of St. Lawrence in Canada where in one instance K= 0.218 and in the other K=0.106 (Clay D. & H. Clay, 1991). These growth rates are compared to survey data gathered by NEFSC.

```{r whitehakeage, echo=FALSE}
##white hake
  #Option1
wh_Linf <- 135 #<-Length
wh_K1 <- 0.218 # <- study 1
wh_K2 <- 0.106 # <- study 2
wh_t <- 0:30 # <- Time
Lengthof_wh1 <- wh_Linf*(1-exp(-wh_K1*wh_t))
Lengthof_wh2 <- wh_Linf*(1-exp(-wh_K2*wh_t))
  #Option2
    #Study1
Lengthof_wh1 <- growthCurve(t= 0:30, k= 0.218, Linf= 133)
    #Study2
Lengthof_wh2 <- growthCurve(t= 0:30, k= 0.106, Linf= 133)

##white hake growth curve
  #Study1
plot(wh_t,Lengthof_wh1,type="l", xlab= "Age (years)", ylab= "Length (cm)",col=c("red"))
  #Study2
points(wh_t,Lengthof_wh2, type="l", xlab= "Age (years)", ylab= "Length (cm)",col=c( "blue"))

#Plotting survey data
points(modifiedData$AGE, modifiedData$LENGTH)

title(main="White Hake (L_inf= 133cm)")
legend(10,30, legend=c("Southern Gulf of St. Lawrence, CA Study 1 (K= 0.218)", "Southern Gulf of St. Lawrence, CA Study 2 (K=0.106)",
                       paste("Survey Data (n=",n,")")),col=c("red", "blue", "black"), lty= c(1, 1, NA), pch= c(NA, NA, 1), cex=0.8)
```

## Distribution of Lengths for Pollock, White Hake, and Red Hake

```{r lengths, echo=FALSE}
datafile <-  read.csv(file="FoodHabits/foodHabits.csv", header=TRUE, sep=",")

modifieddata <- datafile[,c("svspp", "pdlen")]

for (i in c(75,76,77)){
  filt_data  <- modifieddata[modifieddata$svspp == i,]
    if(i==75){
      title <- "Pollock (L_nf=130cm)"
    }else if (i==76){
        title <- "White hake (L_nf= 133cm)" 
      }else if (i==77) {
        title <- "Red hake (L_inf= 66cm)"
      }
  hist(filt_data$pdlen, main = title, xlab="Length (cm)", cex.axis=0.8)
}
```

## Distribution of Mean Stomach Content Volume Across Varying Lengths

```{r stomachs, echo=FALSE, message=FALSE}
datafile <-  read.csv(file="FoodHabits/foodHabits.csv", header=TRUE, sep=",")
modifieddata <- datafile[,c("svspp", "pdlen", "pdswgt")]
library(dplyr)
for (i in c(75,76,77)){
  
  filt_data  <- modifieddata[modifieddata$svspp == i,]
  stomach <- filt_data %>% mutate(interval = cut(pdlen, breaks=10*(0:130), labels= NULL)) %>% 
    group_by(interval) %>%
    summarise(result=mean(pdswgt,na.rm=T))
  if(i==75){
    title <- "Pollock (L_nf=130cm)"
  }else if (i==76){
    title <- "White hake (L_nf= 133cm)"
  }else if (i==77) {
    title <- "Red hake (L_inf= 66cm)"
  }
  
  if(i==75){
    names.arg=c( "0-10", "10-20", "20-30", "30-40", "40-50", "50-60",
                 "60-70", "70-80", "80-90", "90-100", "100-110", "110-120")
    }else if(i==76){
      names.arg=c( "0-10", "10-20", "20-30", "30-40", "40-50", "50-60",
                   "60-70", "70-80", "80-90", "90-100", "100-110", "110-120", "120-130","130-140")
  }else if(i==77){
    names.arg=c( "0-10", "10-20", "20-30", "30-40", "40-50", "50-60","60-70","70-80","80-90")
  }
  barplot(stomach$result, main = title, xlab="Length (cm)", ylab="Stomach Content Volume (g)" , names.arg = names.arg, cex.names=0.5)
}
```